ms_5

### 2020-04-27 Opioid_Crisis_Code.Rmd
renamed

plot_mavsus_death <- ggplot(mavsus_death, aes(x = Year, y = as.numeric(deathperhundredthousand), color = Geography)) +
  geom_line() +
  scale_color_viridis_d() +
theme_classic() +
  labs(x = "Year",
       y = "Deaths per 100,000",
       title = "Comparison of Death Rates between Massachusetts and the United States",
       subtitle = "Between the Years of 2000 and 2014") +
  geom_point() +
  transition_reveal(Year)

@@

ageopioidmodel <- read_csv("U.S. age vs. opioid deaths.csv", col_types = "dcc") %>%
  clean_names() %>%
  na.omit() %>%
  filter(age_range != "Total") %>%
  mutate(age_range = as.factor(age_range)) %>%
    mutate(number_of_deaths = as.numeric(number_of_deaths))

>>>>

plot_mavsus_death <- ggplot(mavsus_death, aes(x = Year, y = as.numeric(deathperhundredthousand), color = Geography)) +
  geom_line() +
  scale_color_viridis_d() +
theme_classic() +
  labs(x = "Year",
       y = "Deaths per 100,000",
       title = "Comparison of Death Rates between Massachusetts and the United States",
       subtitle = "Between the Years of 2000 and 2014") +
  geom_point()

@@

ageopioidmodel <- read_csv("U.S. age vs. opioid deaths.csv", col_types = "dcc") %>%
  clean_names() %>%
  filter(number_of_deaths != "N/A") %>%
  filter(age_range != "Total") %>%
  mutate(age_range = as.factor(age_range)) %>%
    mutate(number_of_deaths = as.numeric(number_of_deaths))
